### 2017-05-02 Paper_v2/Paper_v2.tex
Fixed Bibliography in Paper_v2.

\documentclass[11pt,a4paper]{scrbook}
\usepackage{geometry}	
%\usepackage[backend=bibtex,style=numeric]{biblatex}
%\usepackage{ngerman}
%\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[style=numeric]{biblatex}
\bibliography{../PaperBib2}
\usepackage{colortbl}	
\usepackage{xcolor}
%\usepackage{soul}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[outdir=../Graphen/]{epstopdf}
\usepackage{textcomp}
%\usepackage{floatrow}
\renewcommand{\figurename}{Fig.}
\usepackage[skip=0pt]{caption}
\captionsetup{format=hang}
\setcapindent{0pt}
\usepackage{subcaption}
\usepackage{scrhack}
%\renewcommand{\familydefault}{\sfdefault}
\definecolor{uhhred}{cmyk}{0,100,100,0}
\usepackage{tabularx}

@@

\frontmatter
\newgeometry{centering,left=2cm,right=2cm,top=2cm,bottom=2cm}
\begin{titlepage}
\includegraphics[scale=0.3]{../Graphen/UHH-Logo_2010_Farbe_CMYK.pdf}
\vspace*{2cm}
\Large
\begin{center} 
      {\color{uhhred}\textbf{\so{BACHELORTHESIS}}}
%oder {\color{uhhred}\textbf{\so{MASTERTHESIS}}}
\vspace*{2.0cm}\\
{\LARGE \textbf{Improving the modelling of tempo and phoneme duration}}
\vspace*{2.0cm}\\
vorgelegt von
\vspace*{0.4cm}\\
Alexandra Krah
\end{center}
\vspace*{3.9cm}

\noindent 
MIN-Fakultät \vspace*{0.4cm} \\ 
Fachbereich Informatik \vspace*{0.4cm} \\ 
%Ggf. Professur/Institut \vspace*{0.4cm} \\
Studiengang: Informatik \vspace*{0.4cm} \\ 
Matrikelnummer: 6415559 \vspace*{0.8cm} \\ 
Erstgutachter: Dr. Timo Baumann \vspace*{0.4cm} \\ 
Zweitgutachter: Prof. Dr. Wolfgang Menzel

@@

\printbibliography
\backmatter

>>>>

\documentclass[11pt,a4paper]{scrbook}
\usepackage{geometry}	
%\usepackage[backend=bibtex,style=numeric]{biblatex}
%\usepackage{ngerman}
%\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[style=numeric]{biblatex}
\bibliography{PaperBib}
\usepackage{colortbl}	
\usepackage{xcolor}
%\usepackage{soul}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[outdir=../Graphen/]{epstopdf}
\usepackage{textcomp}
%\usepackage{floatrow}
\renewcommand{\figurename}{Fig.}
\usepackage[skip=0pt]{caption}
\captionsetup{format=hang}
\setcapindent{0pt}
\usepackage{subcaption}
\usepackage{scrhack}
%\renewcommand{\familydefault}{\sfdefault}
\definecolor{uhhred}{cmyk}{0,100,100,0}
\usepackage{tabularx}

@@

\frontmatter
\newgeometry{centering,left=2cm,right=2cm,top=2cm,bottom=2cm}

\begin{titlepage}
\includegraphics[scale=0.3]{../Graphen/UHH-Logo_2010_Farbe_CMYK.pdf}
\vspace*{2cm}
\Large

\begin{center} 
      {\color{uhhred}\textbf{\so{BACHELORTHESIS}}}
	\vspace*{2.0cm}\\
	{\LARGE \textbf{Improving the modelling of tempo and phoneme duration}}
	\vspace*{2.0cm}\\
	vorgelegt von
	\vspace*{0.4cm}\\
	Alexandra Krah
\end{center}

\vspace*{3.9cm}

\noindent 
MIN-Fakultät \vspace*{0.4cm} \\ 
Fachbereich Informatik \vspace*{0.4cm} \\ 
Studiengang: Informatik \vspace*{0.4cm} \\ 
Matrikelnummer: 6415559 \vspace*{0.8cm} \\ 
Erstgutachter: Dr. Timo Baumann \vspace*{0.4cm} \\ 
Zweitgutachter: Prof. Dr. Wolfgang Menzel

@@

\printbibliography

\backmatter
